Implicit yaddayadda

### 2011-10-18 papers/PLDI2012/implicitization.tex
modification des algorithmes dans le papier

@@

\begin{algorithm}
  \begin{algorithmic}
    \STATE \textit{Subset} $\gets \emptyset$
    \WHILE{true}
    \STATE Ascending iteration on \textit{Subset} (lines~\ref{alg=start-ascending}-\ref{alg=end-ascending} in algorithm~\ref{algo:combined})
    \STATE Narrow (line~\ref{alg=narrowing} in algorithm~\ref{algo:combined})
    \STATE Add new paths to \textit{Subset} (lines~\ref{alg=start-add-paths}-\ref{alg=end-add-paths} in algorithm~\ref{algo:combined})
    \ENDWHILE
  \end{algorithmic}
\end{algorithm}

@@

The current working subset of paths, noted $P$, is stored using a
compact representation, such as binary decision diagrams.
We also maintain a set of active control points $A$, containing the points in $P_R$
that still need to be processed. Each time the abstract value of a control point
$p$ is updated, $p$ is inserted in $A$.

We apply the Path-focused technique\cite{Monniaux_Gonnord_SAS11} to
the elements of $A$ until $A$ is empty. 
We also check which paths become feasible, so that we can include them into the
next subset of paths at the next iteration. These new feasible paths are
temporarily stored in a set $P'$. 
When $A$ is empty, it means the
invariant computation of the subgraph is finished. As proposed by
\citet{DBLP:conf/sas/GopanR07}, we can do some narrowing iterations.
These narrowing iterations allow to recover precision lost by
widening, before taking into account new feasible paths.
Thus, our technique combines both the advantages of \emph{Guided Static
Analysis} and \emph{Path-focusing}.
We then restart the analysis with a new subgraph if needed, by adding into $P$
the paths in $P'$. The set of active points $A$ is assigned to $A'$, which is
the set of control points that are starting points of a new feasible path in
$P'$.

@@

This new subgraph is the union of the paths of the previous one with a set
$P'$ of new paths that become feasible regarding the current abstract values.
$P'$ is progressively constructed during the analysis of the subgraph.

We distinguish two phases when analysing a point $p_i \in P_R$:
\begin{enumerate}
\item We search for paths starting at point $p_i$, such that these paths are in
$P$, i.e are included in the working subgraph. Each time we find a path, we
update the abstract value of the destination point of the path. This is the
phase explained in \ref{subsec:ascending}.
\item  When the previous phase terminates, there is no more paths in
$P$, starting at $p_i$, 
that make the abstract values of the successors grow (otherwise, the SMT
solver would not have answered ``\emph{unsat}''). However, there may
exist such paths in the entire multigraph, that are not in $P$. The second phase
computes these paths and adds them to $P'$ (line~\ref{alg=computeNewPaths} in
algorithm~\ref{algo:combined}). We also use SMT solving to discover
these new paths, but we slightly change the SMT formula given to the SMT solver:
we now simply check for the satisfiability of $f(p_i)$ instead of $f(p_i) \wedge
P$. Since we already know that $f(p_i) \wedge P$ is \emph{unsatisfiable}, all
the paths given by the SMT solver won't be in $P$.
\end{enumerate}

>>>>

% commentaires dans les algorithmes crees avec le package algorithmic
\renewcommand{\algorithmiccomment}[1]{ {\color{gray} // #1}}

@@

\begin{algorithm}
  \begin{algorithmic}
    \STATE \textit{Subset} $\gets \emptyset$
    \WHILE{true}
    \STATE Add new paths to \textit{Subset} (lines~\ref{alg=start-add-paths}-\ref{alg=end-add-paths} in algorithm~\ref{algo:combined})
    \STATE Ascending iteration on \textit{Subset} (lines~\ref{alg=start-ascending}-\ref{alg=end-ascending} in algorithm~\ref{algo:combined})
    \STATE Narrow (line~\ref{alg=narrowing} in algorithm~\ref{algo:combined})
    \ENDWHILE
  \end{algorithmic}
\end{algorithm}

@@

The current working subset of paths, noted $P$, is stored using a
compact representation, such as binary decision diagrams.
We also maintain two sets of control points:
\begin{itemize}
	\item $A'$ contains the points in $P_R$ that may be the starting points of new
		feasible paths.
	\item $A$ contains the points in $P_R$ on which we apply the ascending iterations.
	Each time the abstract value of a control point $p$ is updated, $p$ is
	inserted in both $A$ and $A'$.
\end{itemize}

We first check which paths become feasible, so that we can include them into the
next subset of paths. The set $P'$ of new feasible paths is added to the
previous set $P$. Each starting points of paths in $P'$ is added into $A$.
We apply the Path-focused technique\cite{Monniaux_Gonnord_SAS11} to
the elements of $A$ until $A$ is empty. 
When $A$ becomes empty, it means the
invariant computation of the subgraph is finished. As proposed by
\citet{DBLP:conf/sas/GopanR07}, we can do some narrowing iterations.
These narrowing iterations allow to recover precision lost by
widening, before computing and taking into account new feasible paths.
Thus, our technique combines both the advantages of \emph{Guided Static
Analysis} and \emph{Path-focusing}.

After narrowing, we restart the analysis, starting from the computation the new
subgraph.

@@

This new subgraph is the union of the paths of the previous one with a set
$P'$ of new paths that become feasible regarding the current abstract values.

We distinguish two phases when analysing a subgraph $P$:
\begin{enumerate}
\item We search for paths starting at point $p_i \in P_R$, such that these paths
	are in $P$, i.e are included in the working subgraph. Each time we find a
	path, we update the abstract value of the destination point of the path.
	This is the phase explained in \ref{subsec:ascending}.
\item  When the previous phase terminates, there is no more paths in
$P$, starting at $p_i$, 
that make the abstract values of the successors grow (otherwise, the SMT
solver would not have answered ``\emph{unsat}''). Narrowing iterations preserves
this property. 
However, there may exist such paths in the entire multigraph, that are not in
$P$. The second phase
computes these paths and adds them to $P'$ (line~\ref{alg=computeNewPaths} in
algorithm~\ref{algo:combined}). We also use SMT solving to discover
these new paths, but we slightly change the SMT formula given to the SMT solver:
we now simply check for the satisfiability of $f(p_i)$ instead of $f(p_i) \wedge
P$. Since we already know that $f(p_i) \wedge P$ is \emph{unsatisfiable}, all
the paths given by the SMT solver won't be in $P$.
\end{enumerate}
